Versioned data: why it is needed and how it can be achieved (easily and cheaply)

### 2017-09-25 ms.tex
minor changes to discussion

The key features of a \textsc{vdd} system that are already possible are a versioning system to communicate small and large changes to users, both point-and-click and code-based access to all versions, reliable distribution to many users, and stable, organized \textsc{doi}s (see Figure \ref{fig:technology_stack}).  Moreover, it is relatively easy to update and add new versions.  Technology is moving forward rapidly and so it is very likely that the particular tools we describe above will add features and be even easier to use.  But, nonetheless, workable systems are already possible.

One of the greatest benefits of using a cloud-based tool for development of open-source software has been the way it encourages contributions from multiple individuals working simultaneously, and even individuals from outside the initial group of project participants \citep{Rogers-2013}. Multiple users can make changes to different parts of the code (or in our case data) and the \texttt{git} system will integrate these together (if that is possible) or, when needed, flag where there are conflicts that need to be resolved. This makes collaboration easy.

Systematically archiving data is a key part of good workflow \citep{Wilkinson-2016, Piwowar-2011, Whitlock-2011}, and tools for creating and archiving digital objects have seen rapid progress in recent years.  At present, each version of the dataset can be automatically archived and assigned a \textsc{doi}, via several providers (Table \ref{tab:doi_minting}).  Here we describe the particular integration of \texttt{GitHub} and \texttt{Zenodo}.  It is useful to have the ability to either be specific---reference a particular version for the purposes of reproducibility or general--reference the entire project.  \texttt{Zenodo} currently automatically supplies both ``concept'' and ``version'' \textsc{doi}'s to the commits associated with \texttt{GitHub} releases automatically \citep[Figure \ref{fig:semantic} and ][]{Nielsen-2017}.  This allows users to very precisely reference either generally or specifically, both of which may be appropriate in different situations.

>>>>

%The key features of a \textsc{vdd} system that are already possible are a versioning system to communicate small and large changes to users, both point-and-click and code-based access to all versions, reliable distribution to many users, and stable, organized \textsc{doi}s (see Figure \ref{fig:technology_stack}).  Moreover, it is relatively easy to update and add new versions.  Technology is moving forward rapidly and so it is very likely that the particular tools we describe above will add features and be even easier to use.  But, nonetheless, workable systems are already possible.

Additionally, one of the greatest benefits of using a cloud-based tool for development of open-source software has been the way it encourages contributions from multiple individuals working simultaneously, and even individuals from outside the initial group of project participants \citep{Rogers-2013}. Multiple users can make changes to different parts of the code (or in our case, data) and the \texttt{git} system will integrate these together (if that is possible) or, when needed, flag where there are conflicts that need to be resolved. As a result adopting a \textsc{vdd} system has the added benefit of facilitating collaboration among research groups.

%Systematically archiving data is a key part of good workflow \citep{Wilkinson-2016, Piwowar-2011, Whitlock-2011}, and tools for creating and archiving digital objects have seen rapid progress in recent years.  At present, each version of the dataset can be automatically archived and assigned a \textsc{doi}, via several providers (Table \ref{tab:doi_minting}).  Here we describe the particular integration of \texttt{GitHub} and \texttt{Zenodo}.  It is useful to have the ability to either be specific---reference a particular version for the purposes of reproducibility or general--reference the entire project.  \texttt{Zenodo} currently automatically supplies both ``concept'' and ``version'' \textsc{doi}'s to the commits associated with \texttt{GitHub} releases automatically \citep[Figure \ref{fig:semantic} and ][]{Nielsen-2017}.  This allows users to very precisely reference either generally or specifically, both of which may be appropriate in different situations.
